---
title: "Swarm Selection Tutorial"
author: "Peter Hraber"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---


# Phase I: Select Sites

This phase of analysis requires:

1. A protein alignment, provisionally assumed to be in FASTA format.
1. A way to recognize how the longitudinal samples are labeled.  
By default, sequence names are assumed to be dot-delimited,
with the timepoint label in the first (left-most) field.
1. An indication of which sequence is the reference/TF sequence.  
By default, this is taken to be the first sequence in the alignment.

### Choose a Cutoff Setting

We need to choose a setting for the cutoff parameter value.
Let's see how number of sites depends on cutoff threshold.
A vector of cutoff values shows how many sites result from 
multiple settings.  Note that the default values work for these data.

In practice, you will not need to use `system.file()` unless you are 
referring to an example alignment included with the `lassie` package.

```{r, fig.show='hold'}
    library(lassie)
    alignment_file <- system.file("extdata", "CH505-gp160.fasta", package="lassie")
    a <- swarmtools(aas_file=alignment_file, tf_loss_cutoff=0:5*20)
    summary(a)
    plot(a)
```

The 80% cutoff value gives 35 sites.  Let's go with that.

### Having Chosen a Cutoff Setting, List the Selected Sites

```{r echo=FALSE}
    library(lassie)
    alignment_file <- system.file("extdata", "CH505-gp160.fasta", package="lassie")
    A <- swarmtools(aas_file=alignment_file, tf_loss_cutoff=80)
    print(A)
```


# Phase II: Select Clones

This phase of analysis requires a `swarmtools` object created in Phase I.  
The `swarmtools` object must have a list of selected sites, which happens only 
when it was created using a single `tf_loss_cutoff` value.

Let's just go with the defaults.

    B <- swarmset(A, is_verbose=F)


# All Together Now

Here's the whole workflow:

```{r, fig.show='hold'}
    library(lassie)
    alignment_file <- system.file("extdata", "CH505-gp160.fasta", package="lassie")
    a <- swarmtools(aas_file=alignment_file, tf_loss_cutoff=0:5*20)
    summary(a)
    A <- swarmtools(aas_file=alignment_file, tf_loss_cutoff=80)
    print(A)
    B <- swarmset(A)
    summary(B)
    print(B)
    b.plot <- plot(B)
```

***
